Tropical Andes plant occurrence data GBIF

### 2025-08-27 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
Source function fix

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
source("~/GitHub/neotropical_plants/functions/data_summary.R")
```

>>>>

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
source("C:/GitHub_projects/plant-frugivore diversity/neotropical_plants/code/data_summary.R")
```
